---
title: "Oral Presentation 3"
subtitle: "Estimation Results and Interpretation"
author: "D. Goninet, T. Lezoualc'h, V. Martre"
date: "February 12th, 2018"

output:
  beamer_presentation:
    slide_level: 1
    toc: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Economic Question

\center

**In what extent happiness is linked to GDP per capita?**


| Variables                   | Description                 |
|-----------------------------|-----------------------------|
| Happiness                   | Between 4 and 7 in our data |
| $log$(GDP per capita)       |                             |
| GINI Index                  |                             |
| CO2 emissions               |                             |
| Continent                   | 5 groups: Europe,           |
| Numb. of children per woman |                             |


# A simple model
## Enoncer le modèle (écrire son équation)
## Le justifier
## Montrer les résultats (table des coefficients)
## Donner les interprétations (effet marginal, élasticités, etc.)
## Relier les conclusions à la problématique

<!--
## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```
-->