---
title: "Oral Presentation 3"
subtitle: "Estimation Results and Interpretation"
author: "D. Goninet, T. Lezoualc'h, V. Martre"
date: "February 12th, 2018"

output:
  beamer_presentation:
    slide_level: 1
    toc: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

load.libraries <- c('gdata', 'ggplot2', 'xlsx', 'MNP', 'psych', 'foreign', 'nnet', 'reshape2', 'xtable', 'knitr')
install.lib <- load.libraries[!load.libraries %in% installed.packages()]
for(libs in install.lib) install.packages(libs, dependencies = TRUE)
sapply(load.libraries, require, character = TRUE)

finaldata <- read.xlsx('database-whr17-v6.xlsx', 1)
finaldata$RLadder <- as.factor(finaldata$RLadder)
finaldata$Continent <- as.factor(finaldata$Continent)
finaldata$RLadder2 <- relevel(finaldata$RLadder, ref ="4")

test1 <- multinom(RLadder2 ~ GDP, finaldata)
test2 <- multinom(RLadder2 ~ GDP + GINI + CO2 + Continent + CPW, data = finaldata)

```

# Economic Question

\center

**In what extent happiness is linked to GDP per capita?**


| Variables                   | Description                                     |
|-----------------------------|-------------------------------------------------|
| ```RLadder```               | Level of Happiness: between 4 and 7 in our data |
| ```GDP```                | The log of GDP per capita                       |
| ```GINI```                  | The GINI Index                                  |
| ```CO2 emissions```         | CO2 emissions                                   |
| ```Continent```             | 5 groups: Europe,                               |
| ```CPW```                   | Numb. of children per woman                     |


# A simple model

\center

```RLadder``` $= \beta_{0} + \beta_{1} \cdot$ ```logGDP```


```{r 1.coefftable, results="asis"}
t1 <- xtable(summary(test1)$coefficients)
print(t1, type="latex", comment = FALSE)
```

$ln \frac{P(RLadder = 5)}{P(RLadder = 4)} = b_{10} + b_{11}GDP$

$ln \frac{P(RLadder = 6)}{P(RLadder = 4)} = b_{20} + b_{21}GDP$

$ln \frac{P(RLadder = 7)}{P(RLadder = 4)} = b_{30} + b_{31}GDP$

# Multinomial Logit Model

\center

```RLadder``` $= \beta_{0} + \beta_{1} \cdot$ ```GDP``` + $\beta_{2} \cdot$ ```GINI``` + $\beta_{3} \cdot$ ```CO2``` + $\beta_{4} \cdot$ ```Continent``` + $\beta_{5} \cdot$ ```CPW```

```{r 2.coefftable, results="asis"}
t2 <- xtable(summary(test2)$coefficients, auto = TRUE)
digits(t2) <- 2
print(t2, type="latex", comment = FALSE)
```

$ln \frac{P(RLadder = 5)}{P(RLadder = 4)} = b_{10} + b_{11}GDP + b_{21}GINI + b_{31}CO2 + b_{41}(Continent = 1) + ... + b{71}CPW$

## Donner les interprétations (effet marginal, élasticités, etc.)
## Relier les conclusions à la problématique

<!--
## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```
-->